Austraits – a curated plant trait database for the Australian flora

### 2018-07-17 ms.Rmd
Add template style.

---
title: "Austraits – a curated plant trait database for the Australian flora"
bibliography: references.bib
csl: nature.csl  
output:
  word_document: default
  pdf_document:
    keep_tex: yes
  html_document: default
geometry: margin=0.75in
fontsize: 9pt
editor_options:
  chunk_output_type: console
---

@@

# print list of authors
sprintf("%s (%s)", authors$Author, authors$label) %>% paste0(collapse = ", ") %>% writeLines()

@@

# print list of affiliations
sprintf("**%s**- %s", affils$label, affils$Affiliation) %>% paste0(collapse = "; ") %>% writeLines()
```

>>>>

---
title: "Austraits – a curated plant trait database for the Australian flora"
bibliography: references.bib
csl: assets/nature.csl  
output:
  word_document:
    reference_docx: assets/manuscriptstyle.docx
  html_document:
    number_sections: yes
    theme: flatly
  pdf_document:
    keep_tex: no
geometry: margin=0.75in
fontsize: 9pt
editor_options:
  chunk_output_type: console
---

@@

# print list of authors
sprintf("%s^%s^", authors$Author, authors$label) %>% paste0(collapse = ", ") %>% writeLines()

@@

# print list of affiliations
sprintf("^%s^ %s", affils$label, affils$Affiliation) %>% paste0(collapse = "; ") %>% writeLines()
```
